---
sidebar: false
toc: false
---

# Workshop_title

| Audience | Computational skills required| Duration |
:----------|:----------|:----------|
| Biologists | [Workshop pre-requisite]() | 4-session online workshop (8 hours of trainer-led time)|

### Description

This repository has teaching materials for a hands-on workshop on **Workshop Name**. Description of workshop. 

::: calout-note
# Note for Trainers:
Please note that the schedule linked below assumes that learners will spend between 3-5 hours on reading through and completing exercises from selected lessons between classes. The online component of the workshop focuses on more exercises and discussion/Q & A.
:::

::: callout-note
These materials were developed for a trainer-led workshop, but are also amenable to self-guided learning.
:::

### Learning Objectives

In this workshop, the participants will:

- Broad Learning Objective 1
- Broad Learning Objective 2
- Broad Learning Objective 3
- Broad Learning Objective 4

### Lessons
* [Workshop schedule (trainer-led learning)](schedule/schedule.qmd)
* [Self-learning](schedule/self-learning.qmd)

### Installation Requirements (shell-based)
***All:***

***Mac users:***
No additional installation requirements.  

***Windows users:***
[GitBash](https://git-scm.com/download/win)  

### Installation Requirements (R-based)

#### Applications
Download the most recent versions of R and RStudio for your laptop:

 - [R](http://lib.stat.cmu.edu/R/CRAN/) **(version 4.3.0 or above)**
 - [RStudio](https://www.rstudio.com/products/rstudio/download/#download)

#### Packages for R

> **Note 1: Install the packages in the order listed below.**

> **Note 2:  All the package names listed below are case sensitive!**

> **Note 3**: **If you have a Mac,** download and install this tool before installing your packages if using R versions 4.3.0 up to 4.4.3:
https://mac.r-project.org/tools/gfortran-12.2-universal.pkg
And this tool if using R versions after 4.4.3:
https://mac.r-project.org/tools/gfortran-14.2-universal.pkg

> **Note 4**: At any point (especially if you’ve used R/Bioconductor in the past), in the console **R may ask you if you want to update any old packages by asking Update all/some/none? [a/s/n]:**. If you see this, **type "a" at the prompt and hit Enter** to update any old packages. _Updating packages can sometimes take quite a bit of time to run, so please account for that before you start with these installations._  

> **Note 5:** If you see a message in your console along the lines of “binary version available but the source version is later”, followed by a question, **“Do you want to install from sources the package which needs compilation? y/n”, type n for no, and hit enter**.

**(1)** Install the X packages listed below from **CRAN** using the `install.packages()` function. 

1. BiocManager
2. ..
3. ...

**Please install them one-by-one as follows:**

```{r}
#| label: install_CRAN_packages
#| eval: false
install.packages("BiocManager")
install.packages("package_name")
install.packages("package_name")
```

**(2)** Install the X packages listed below from **Bioconductor** using the the `BiocManager::install()` function.

1. ..
2. ..

**Please install them one-by-one as follows:**

```{r}
#| label: install_bioconductor_packages
#| eval: false
BiocManager::install("package_name")
BiocManager::install("package_name")
BiocManager::install("package_name")
```

**(3)** Finally, please check that all the packages were installed successfully by **loading them one at a time** using the `library()` function.  

```{r}
#| label: load_libraries
#| eval: false
library(package_name)
library(package_name)
library(package_name)
library(package_name)
library(package_name)
library(package_name)
```

**(4)** Once all packages have been loaded, run sessionInfo().  

```{r}
#| label: print_sessionInfo
#| eval: false
sessionInfo()
```

***

*These materials have been developed by members of the teaching team at the [Harvard Chan Bioinformatics Core (HBC)](http://bioinformatics.sph.harvard.edu/). These are open access materials distributed under the terms of the [Creative Commons Attribution license](https://creativecommons.org/licenses/by/4.0/) (CC BY 4.0), which permits unrestricted use, distribution, and reproduction in any medium, provided the original author and source are credited.*
